---
title       : Course Project final assignment
subtitle    : Shiny Application and Reproducible Pitch
author      : Tiago Carvalho
job         : 
framework   : shower        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Guess the number - Summary

My assignment is not an analysis _per se_, but I hope it is fun to try out
In this interface you're playing a game of guessing a random generated number between 1 and 100

--- .class #id 

## References 

The game can be played at https://tiagosgc.shinyapps.io/final/
This documentation is hosted @ https://github.com/tiagosgc/finalDeck/

---

## Why 7 tries?

If you eliminate half of the possible numbers in each try, you should always be able to guess in 7 tries


---

## Some code to demonstrate my point

```{r, eval=FALSE}
n<-100
i<-c(1,2,3,4,5,6,7)
for (val in i) {
    n <- ceiling(n/2)
    print(paste(c("Iteration ", val,
        ", number of possible answers reduced to ",
        n),collapse = ''))
    
}

```

---

## And the same code output

```{r, eval=TRUE, echo =FALSE, comment=''}
n<-100
i<-c(1,2,3,4,5,6,7)
for (val in i) {
    n <- ceiling(n/2)
    print(paste(c("Iteration ", val,
        ", # possible answers = ",
        n),collapse = ''))
    
}

```






